\begin{thebibliography}{20}

\bibitem{art1}Margaret Rouse, TechTarget(2018, September).
\emph{Cryptography}[article],\\
Available: {https://searchsecurity.techtarget.com/definition/cryptography}

\bibitem{art2} Records Keeper(2018).
\emph{Verify Academic Certifications}[article],\\
Available: {https://www.recordskeeper.co/verify-academic-certifications/}

\bibitem{art3} Tony Mushoborozi, Daily Monitor (2018, Monday October 1).
\emph{The scourge of fake academic papers}[article],\\
Available: {https://www.monitor.co.ug/News/Education/jobs-dark-world-fake-academic-documents/688336-4784694-bvjkc7z/index.html}

\bibitem{art4} Isaac Mufumba, Daily Monitor (2018, Wednesday July 4 ).
\emph{High youth unemployment persists despite entrepreneurship training}[article],\\
Available: {https://www.monitor.co.ug/SpecialReports/High-youth-unemployment-persists-entrepreneurship-training/688342-4644926-563r8fz/index.html}

\bibitem{art5} Knoema Corporation (2017).
\emph{Uganda Literacy Rate}[article],\\
Available: {https://knoema.com/atlas/Uganda/topics/Education/Literacy/Adult-literacy-rate}

\bibitem{art6} Blocksign (2019).
\emph{Blocksign}\\
Available: {https://blocksign.com/}

\bibitem{art7} SiaDocs (2019, May).
\emph{Siacoin Documentation}\\
Available: {https://sia.tech/docs}

\bibitem{art8} Bennet Garner (2018, February 14).
\emph{What is Storj? - Beginner’s Guide}[article],\\
Available: {https://coincentral.com/storj-beginners-guide/}

\bibitem{art9} Ethereum Project (2019).
\emph{Blockchain platform to run smart contracts as they are coded to be}\\
Available: {https://www.ethereum.org}

\bibitem{art10} Cryptyk Inc. (2019).
\emph{Cryptyk}\\
Available: {https://www.cryptyk.io/}

\bibitem{art11}Luke Graham, CNBC News (2016, May).
\emph{Schools are using bitcoin technology to track students:}[article],\\
Available: {https://www.cnbc.com/2016/05/09/schools-are-recording-students-results-on-the-blockchain.html}

\bibitem{art12}Donald Clark, OEB Global (2016, September 12).
\emph{10 ways Blockchain could be used in education}[article],\\
Available: {https://oeb.global/oeb-insights/10-ways-blockchain-could-be-used-in-education}

\bibitem{art13}  Jeanne Segal, Ph.D., Melinda Smith, M.A., Lawrence Robinson, and Greg Boose. (2019, May)
\emph{Nonverbal Communication}[article],\\
Available: {https://www.helpguide.org/articles/relationships-communication/nonverbal-communication.htm/}

\bibitem{art14}
\emph{Google Sheets… Daily Stand-Up Meeting Notes},\\
Available: {https://docs.google.com/spreadsheets/d/15UG7nM81GFjQZ-RqAL8cjWwyJkyvfk6Rtrpx5KBhQtw/edit?usp=sharing}

\bibitem{art15} Wikipedia (2019, May 31)
\emph{Hash function}[article],\\
Available: {https://en.wikipedia.org/wiki/Hash\_function/}

\bibitem{art16}Protocol labs (2019)
\emph{InterPlanetary File System},\\
Available: {https://ipfs.io}

\bibitem{art17} Truffle Blockchain Group (2019)
\emph{Ganache… A one click blockchain},\\
Available: {https://truffleframework.com/ganache}

\bibitem{art18} Wikipedia (2019, May 22)
\emph{Decentralized application}[article],\\
Available: {https://en.wikipedia.org/wiki/Decentralized\_application}

\bibitem{art19} Bitcoin Magazine (2019).
\emph{What is ether?}[article],\\
Available: {https://bitcoinmagazine.com/guides/what-ether/}

\bibitem{art20}Wikipedia (2019, May 10)
\emph{Directed acyclic graph}[article],\\
Available: {https://en.wikipedia.org/wiki/Directed\_acyclic\_graph}

\bibitem{art21}
\emph{Ethereum Wallet - What is a wallet, and which one should I use?}[article],\\
Available: {https://www.ethereum.org/use/}

\end{thebibliography}

